\papertitle

### 2013-01-19 manuscript.tex
fixed the strange figure text sizes
edits

@@

We approximate the yaw dynamics of the ornithopter with a one-dimensional 
model to limit complexity, and because it matches our physical 
implementation. Likewise, we choose the reference heading angle as the input to 
the model, and model the dynamics of vehicle and on-board PID controller as 
one system, whose output is the physical heading angle:
\begin{equation}
\label{eq:plain_model}
\begin{aligned}
& H(s) = \frac{K}{1 + Rs}
& \text{where }H(s) = \frac{\theta(s)}{u(s)}
\end{aligned}
\end{equation}
To model the translational position of the ornithopter, we use a form of 
Dubin's car model~\cite{lavalle:planning}: 
\begin{equation}
\label{eq:dubin_car}
\begin{aligned}
& \dot{x} = u_{s}sin(\theta)\\
& \dot{y} = u_{s}cos(\theta)\\
& \dot{\theta} = u\\
& u \in U=[-\tan{\phi_{max}},\tan{\phi_{max}}]
\end{aligned}
\end{equation} 
In the car model, $\phi_{max}$ is the maximum steering angle and $u_{s}$ is
the forward speed. We modify this model to treat the angular position $\theta$
as an input rather than a state. The overall motion of the system can be
modeled as shown in Equation~\ref{eq:dubin_car}, where $\theta$ is the
time-domain output of Equation~\ref{eq:plain_model}, $\theta(t)$, with the
reference heading angle, $u(t)$, as input.

@@

We model the viewing angle of the camera as a pixel map from one edge of a 
63$^{\circ}$ viewing triangle to the other. The camera has an image width of 
640 pixels. We calculate the desired heading angle in degrees, for a given 
distance from the camera, according to Equation~\ref{eq:desired_heading}.
\begin{equation} 
\label{eq:desired_heading} 
\text{Desired heading} = \frac{640\,\text{px}}{2d\tan{\frac{63^{\circ}}{2}}}{\times\frac{63^{\circ}}{640\,\text{px}}\times x}
\end{equation}
where $d$ is the distance between the ornithopter and the camera, and $x$ is 
the horizontal position of the robot relative to the center of the window in 
meters. This relation reflects the fact that the pose estimation algorithm 
does not determine the depth of the robot, which can be problematic for 
control algorithms. For example, if the ornithopter remains at a constant 
horizontal distance from the window, but moves closer and closer to the 
camera, the ground station's directed heading steadily increases, even 
though the robot has not actually moved farther from the window. These 
problems are most severe in areas close to the camera.

>>>>

In this section, we describe the models that we developed to simulate the
behaviors of the ornithopter and the ground station. We use these models to
determine the set of initial conditions that are most likely to result in
successful window traversal.

@@

We approximate the yaw dynamics of the ornithopter with a one-dimensional 
model to limit complexity, and because it matches our physical 
implementation:
\begin{equation}
\label{eq:plain_model}
\begin{aligned}
& H(s) = \frac{K}{1 + Rs}
& \text{where }H(s) = \frac{\theta(s)}{u(s)}
\end{aligned}
\end{equation}
We choose the reference heading angle as the input to the model, $u(s)$, and
model the dynamics of vehicle and on-board PID controller as one system, whose
output is the physical heading angle, $\theta(s)$. To model the translational position of
the ornithopter, we use a form of Dubin's car model~\cite{lavalle:planning}:
\begin{equation}
\label{eq:dubin_car}
\begin{aligned}
& \dot{x} = u_{s}sin(\theta)\\
& \dot{y} = u_{s}cos(\theta)\\
& \dot{\theta} = u\\
& u \in U=[-\tan{\phi_{max}},\tan{\phi_{max}}]
\end{aligned}
\end{equation} 
In the car model, $\phi_{max}$ is the maximum steering angle and $u_{s}$ is
the forward speed. We modify this model to treat the angular position $\theta$
as an input rather than a state. The overall motion of the system can be
modeled as shown in Equation~\ref{eq:dubin_car}, where $\theta$ is the
time-domain output of Equation~\ref{eq:plain_model}, $\theta(t)$.

@@

We model the viewing angle of the camera as a pixel map from one edge of a 
63$^{\circ}$ viewing triangle to the other. The camera has an image width of 
640 pixels. We calculate the desired heading angle in degrees, for a given 
distance from the camera:
\begin{equation} 
\label{eq:desired_heading} 
\text{Desired heading} = \frac{640\,\text{px}}{2d\tan{\frac{63^{\circ}}{2}}}{\times\frac{63^{\circ}}{640\,\text{px}}\times x}
\end{equation}
where $d$ is the distance between the ornithopter and the camera, and $x$ is 
the horizontal position of the robot relative to the center of the window in 
meters. This relation reflects the fact that the pose estimation algorithm 
does not determine the depth of the robot, which can be problematic for 
control algorithms. For example, if the ornithopter remains at a constant 
horizontal distance from the window, but moves closer and closer to the 
camera, the ground station's directed heading steadily increases, even 
though the robot has not actually moved farther from the window. These 
problems are most severe in areas close to the camera.
